---
title: "Rworksheet#3b"
author: "Lance Y. Sarabia"
date: "2022-11-23"
output: pdf_document
---

h\fillbreak
1. Create a data frame using the table below.
a. Write the codes.
```{r, include=TRUE}
data1 <- data.frame(Respondents = c(seq(1:20)),
                    Sex = c(2,2,1,2,2,2,2,2,2,2,1,2,2,2,2,2,2,2,1,2),
                    Fathers_Occupation = c(1,3,3,3,1,2,3,1,1,1,3,2,1,3,3,1,3,1,2,1),
                    Persons_at_home = c(5,7,3,8,5,9,6,7,8,4,7,5,4,7,8,8,3,11,7,6),
                    Siblings_at_school = c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2),
                    Types_of_houses = c(1,2,3,1,1,3,3,1,2,3,2,3,2,2,3,3,3,3,3,2)
)
data1
```
h\fillbreak
b.Describe the data. Get the structure or the summary of the data
```{r, include= TRUE}
sum_data1 <- summary(data1)
sum_data1
```
h\fillbreak
c. Is the mean number of siblings attending is 5? - No, the mean of siblings at school is 2.95

h\fillbreak
d. Extract the 1st two rows and then all the columns using the subsetting functions.
Write the codes and its output.
```{r, include= TRUE}
sub_data1 <- subset(data1[1:2, 1:6])
sub_data1
```
h\fillbreak
e. Extract 3rd and 5th row with 2nd and 4th column. Write the codes and its result.
```{r, include= TRUE}
sub_data2 <- subset(data1[c(3,5),c(2,4)])
sub_data2
```
h\fillbreak
f. Select the variable types of houses then store the vector that results as types_houses. Write the codes.
```{r, include= TRUE}
sub_data3 <- c(data1$Types_of_houses)
sub_data3

types_houses <- sub_data3
types_houses
```
h\fillbreak
g. Select only all Males respondent that their father occupation was farmer. Write the codes and its output.
```{r, include= TRUE}
sub_data4 <- subset(data1[c(1:20), c(2,3)])
sub_data4

data_male <- sub_data4[data1$Fathers_Occupation == '1',]
data_male
```
h\fillbreak
h. Select only all females respondent that have greater than or equal to 5 number of siblings attending school. Write the codes and its outputs.
```{r, include= TRUE}
sub_data5 <- subset(data1[c(1:20), c(2,5)])
sub_data5

data_female <- sub_data5[data1$Siblings_at_school >= '5',]
data_female
```
h\fillbreak
2. Write a R program to create an empty data frame. Using the following codes:
```{r, include= TRUE}
df = data.frame(Ints=integer(),
                Doubles=double(), Characters=character(),
                Logicals=logical(),
                Factors=factor(),
                stringsAsFactors=FALSE)
paste("Structure of the empty dataframe:")
paste(str(df))
```
h\fillbreak
a. Describe the results. - The data shows that there is no rows but has 5 columns with zero(0) factor levels.

h\fillbreak
3. Interpret the graph. -From the data it shows that there is more negative tweets than the neutral and positive, and it skewed from left to right within the timeframe of july 15, 2020 - july 21, 2020.

