---
title: "Rworksheet#6"
author: "Lance Y. Sarabia"
date: "2022-11-25"
output: pdf_document
---

---
title: "Rworksheet#6"
author: "Lance Y. Sarabia"
date: "2022-11-25"
output: pdf_document
---

```{r, include= TRUE}
library(ggplot2)
library(dplyr)

data(mpg)

data2 <- as.data.frame(mpg)
data2
```
\hfill\break
1. How many columns are in mpg dataset? How about the number of rows? Show thecodes and its result.
  #ans - it has 11 columns and a rows of 234
```{r, include= TRUE}
  mpg_data <- glimpse(data2)
```
\hfill\break
2. Which manufacturer has the most models in this data set? Which model has the most variations? ans - the manufacturer that has the most model are the Dodge while the most variations for model are the caravan2wd
```{r, include= TRUE}
  manufact <- mpg_data %>% group_by(manufacturer,model) %>% count()
  manufact
  
  colnames(manufact) <- c("Manufacturer", "Model", "Counts")
  
```
\hfill\break
a. Group the manufacturers and find the unique models. Copy the codes and result.
```{r, include= TRUE}
  data_unique <- mpg_data %>% group_by(manufacturer) %>% 
    distinct(model) %>% count()
  data_unique
 
  colnames(data_unique) <- c("Manufacturer", "Unique Counts")
```
\hfill\break
b. Graph the result by using plot() and ggplot(). Write the codes and its result.
```{r, echo=TRUE}
plot(manufact)
```

```{r, echo=TRUE}
ggplot(manufact, aes(Manufacturer, Model)) + geom_point()
```
\hfill\break
3. Same dataset will be used. You are going to show the relationship of the model and the manufacturer.
a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show? ans - A point graph of model and manufacturer from the mpg data-set that will let the user analyze the data easily
```{r, include= TRUE}
  ggplot(data2, aes(model, manufacturer)) + geom_point()
```
\hfill\break
b. For you, is it useful? If not, how could you modify the data to make it more informative? ans - Although the data is already organized, it can still be improved to look more informative 
by adding a legend to easily distinguish the data from the scatter plot.

\hfill\break
4. Using the pipe (%>%), group the model and get the number of cars per model. Show codes and its result.
```{r, include= TRUE}
  car_model <- mpg_data %>% group_by(model) %>% count()
  car_model
  
  colnames(car_model) <- c("Model", "Counts")
```
\hfill\break
a. Plot using the geom_bar() + coord_flip() just like what is shown below. Show codes and its result.
```{r, include= TRUE}
  qplot(model,data = data2, 
  main = "Number of Cars per Model",
  xlab = "Model",
  ylab = "Number of Cars", geom = "bar", fill = manufacturer) + coord_flip()
```
\hfill\break
b. Use only the top 20 observations. Show code and results.
```{r, include= TRUE}
  top_data <- car_model[1:20,] %>% top_n(2)
  top_data

  ggplot(top_data,aes(x = Model, y = Counts)) + 
    geom_bar(stat = "Identity") +coord_flip()
```
\hfill\break
5. Plot the relationship between cyl - number of cylinders and displ - engine displacement using geom_point with aesthetic colour = engine displacement. Title should be “Relationship between No. of Cylinders and Engine Displacement”.
a. Show the codes and its result.
```{r, include= TRUE}
  ggplot(data = mpg_data , mapping = aes(x = displ, y = cyl, main = "Relationship 
                                    between No of Cylinders and 
                                    Engine Displacement")) + 
  geom_point(mapping=aes(colour = "engine displacement")) 
```
\hfill\break
b. How would you describe its relationship?
ans - the scatter plot shows that the cyl is in y axis and the displ are in the x axis
to easily distinguish the clustered data, wchich indicate the engine displacement.

\hfill\break
6. Get the total number of observations for drv - type of drive train (f = front-wheel drive,
r = rear wheel drive, 4 = 4wd) and class - type of class (Example: suv, 2seater, etc.).

Plot using the geom_tile() where the number of observations for class be used as a fill for aesthetics.
a. Show the codes and its result for the narrative in #6.
```{r, include= TRUE}
  ggplot(data = mpg_data, mapping = aes(x = drv, y = class)) +
    geom_tile(aes(fill=class))
```
\hfill\break
b. Interpret the result.
ans - by mapping a geometric tile, it graph the data in a tile graph that was shown in diffrent colors, the drv are in the X axis while the class are in the Y axis.
\hfill\break
7. Discuss the difference between these codes. Its outputs for each are shown below.
ans - the graph are almost the same but the first code are much easier to analyze since it has a legend that can distinguish the jittered data while the second code are only in a graph that has a color blue.
```{r, include= TRUE}
#first code
  ggplot(data = mpg) +
    geom_point(mapping = aes(x = displ, y = hwy, colour = "blue"))
```

```{r, include= TRUE}
#second code
  ggplot(data = mpg) +
    geom_point(mapping = aes(x = displ, y = hwy), colour = "blue")
```  
\hfill\break
8. Try to run the command ?mpg. What is the result of this command? ans - the result are in the help option, it shows the description for the data set of mpg.
```{r, include= TRUE}
  cmd1 <-?mpg
  cmd1
```
a. Which variables from mpg dataset are categorical? ans - the manufacturer, model, trans, drv, fl, class are the categorical variables from the data-set of mpg.
  
b. Which are continuous variables?
ans - the consinuous variable of the mpg data-set are the dsipl, year, cyl, cty, and hwy.
  
c. Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon). 
Mapped it with a continuous variable you have identified in #5-b. What is its result? Why it produced such output? ans - the data the have been graph shows that they are in the positive rate using the displ for hwy and cty scattered plot.

```{r, include= TRUE}
  ggplot(mpg, aes(x = cty, y = hwy, colour = displ)) + geom_point()
```
\hfill\break
9. Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon) using geom_point(). Add a trend line over the existing plot using geom_smooth() with se = FALSE. Default method is “loess”.
```{r, include= TRUE}
  ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
    geom_point(mapping=aes(color=class)) +
    geom_smooth(se = FALSE)
``` 
\hfill\break
10. Using the relationship of displ and hwy, add a trend line over existing 
plot. Set these = FALSE to remove the confidence interval and method = lm to check for linear modeling.
```{r, include= TRUE}
  ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = class)) +
    geom_point() +
    geom_smooth(se = FALSE, method = lm)
```
