---
title: "Rworksheet#4"
author: "Lance Y. Sarabia"
date: "2022-11-23"
output: pdf_document
---

\hfill\break
1. The table below shows the data about shoe size and height. Create a data frame.
```{r, include= TRUE}
Shoesize1 <- c(6.5,9.0,8.5,8.5,10.5,7.0,9.5,9.0,13.0,7.5,10.5,8.5,12.0,10.5,13.0,11.5,8.5,5.0,10.0,6.5,7.5,8.5,10.5,8.5,10.5,11.0,9.0,13.0)
Height1 <- c(66.0,68.0,64.5,65.0,70.0,64.0,70.0,71.0,72.0,64.0,74.5,67.0,71.0,71.0,77.0,72.0,59.0,62.0,72.0,66.0,64.0,67.0,73.0,69.0,72.0,70.0,69.0,70.0)
Gender1 <- c("F","F","F","F","M","F","F","F","M","F","M","F","M","M","M","M","F","F","M","F","F","M","M","F","M","M","M","M")

data1_df <- data.frame(Shoesize1, Height1, Gender1)
data1_df
```
\hfill\break
a. Describe the data. - The data shows the different shoesize of male and female with its different heights from 2 data from the dataframe.

\hfill\break
b. Find the mean of shoe size and height of the respondents. Copy the codes and results.
```{r, include= TRUE}
data_mean1 <- mean(Shoesize1)
data_mean1

mean_heights <- mean(Height1)
mean_heights
```
\hfill\break
c. Is there a relationship between shoe size and height? Why? - Yes, there is a correlation between shoe size and height; larger shoes are preferred by taller individuals. The respondents' shoe size will be tiny if their height is less than 70.0.

\hfill\break
 Factors
2.Construct character vector months to a factor with factor() and assign the result to factor_months_vector. Print out factor_months_vector and assert that R prints out the factor levels below the actual values.Consider data consisting of the names of months:
```{r, include= TRUE}
months1 <- c("March","April","January","November","January","September","October","September","November","August","January","November","November","February","May","August","July","December","August","August","September","November","February","April")
months1

factor_months <- factor(months1)
factor_months
```
\hfill\break
3. Then check the summary() of the months_vector and factor_months_vector. Interpret the results of both vectors. Are they both equally useful in this case?
Yes, they are useful as they count how many repeated data your variable have, and not do it manually.
```{r, include= TRUE}
sum_months1 <- summary(months1)
sum_months1

sum_fact_months <- summary(factor_months)
sum_fact_months
```
\hfill\break
4. Create a vector and factor for the table below.
```{r, include= TRUE}
data_fact <- c("East" = '1', "West" = '4', "North" = '3')
data_fact

new_order_data <- factor(data_fact,levels = c("East" = '1',  "West" = '4',  "North" = '3'))
print(new_order_data)
```
\hfill\break
5. Enter the data below in Excel with file name = import_march.csv
```{r, include= TRUE}
data_tab <- read.table("/cloud/project/Rworksheet4/import_march.csv", header=TRUE, sep = ",")
data_tab
```
b. read the data set. write the code and it's result.
```{r, include= TRUE}
tab <- read.csv("/cloud/project/Rworksheet4/import_march.csv")
tab
```