---
title: "Rworksheet#5"
author: "Lance Y. Sarabia"
date: "2022-11-23"
output: pdf_document
---
\hfill\break
1. The table shows the enrollment of BS in Computer Science, SY 2010-2011.
```{r, include= TRUE}
enroll <- data.frame("Course Year" = c ("1st", "2nd", "3rd", "4th"), " 2019–2020" = c(80, 75, 70, 60))
enroll
```
\hfill\break
a. Plot the data using a bar graph. Write the codes and copy the result.
```{r, include= TRUE}
bar_data <- c("1st" = 80, "2nd" = 75, "3rd" = 70, "4th" = 60)
bar_data
barplot(bar_data)
```
\hfill\break
b. Using the same table, label the barchart with Title = ” Enrollment of BS Computer Science" horizontal axis = “Curriculum Year” and vertical axis = “number of students”
```{r, include= TRUE}
bar_tab <- c("1st" = 80 , "2nd" = 75, "3rd" = 70, "4th" = 60)
bar_tab
barplot(bar_tab, 
        main = "Enrollment of BS Computer Science", 
        xlab = "Curriculum Year", 
        ylab = "Number of Students")
```
\hfill\break
2. The monthly income of De Jesus family was spent on the following: 60% on Food, 10% on electricity, 5% for savings, and 25% for other miscellaneous expenses.
a. Create a table for the above scenario. Write the codes and its result.
```{r, include= TRUE}
month_data <- data.frame(
  facts = c("Food", "Electricity", "Savings", "Miscellaneous_expenses"),
  spent = c(60, 10, 5, 25)
)
month_data
tab_data <- table(month_data)
tab_data
```
\hfill\break
b. Plot the data using a pie chart. Add labels, colors and legend. Write the codes and its result.
```{r, include= TRUE}
 spent = c(60, 10, 5, 25)
data_per <- round(spent/sum(spent) * 100, 1)
data_per <- paste(data_per,"%",sep = "")

data_pie <- pie(spent,
    main = "Month Data",
    col = rainbow(4),
    labels =  data_per, cex = 0.8)
data_pie

legend(1.0,0.8, c("Food","Electricity","Savings","Miscellaneous expenses"),
       cex = 0.8,fill = rainbow(4))
```
\hfill\break
3. Open the mtcars dataset.
a. Create a simple histogram specifically for mpg (miles per gallon) variable. Use $ to select the mpg only. Write the codes and its result.
```{r, include= TRUE}
data("mtcars")
data_mtcars <- (mtcars$mpg)
data_mtcars

hist(data_mtcars, breaks = 12)
```
\hfill\break
b. Colored histogram with different number of bins. 
hist(mtcars$mpg, breaks=12, col="red") Note: breaks= controls the number of bins.
```{r, include= TRUE}
hist(data_mtcars, breaks=12, col="blue")
```
\hfill\break
c. Add a Normal Curve x <- mtcars$mpg
h<-hist(x, breaks=10, col="red", xlab="Miles Per Gallon", main="Histogram with Normal Curve") xfit<-seq(min(x),max(x),length=40) yfit<-dnorm(xfit,mean=mean(x),sd=sd(x)) yfit <- yfit*diff(h$mids[1:2])*length(x) lines(xfit, yfit, col="blue", lwd=2) Copy the result.
data_curve <- data_mtcars
data_curve
```{r, include= TRUE}
data_hist <-hist(data_curve, breaks=10, col="red", xlab="Miles Per Gallon",
    main="Histogram with Normal Curve")
    xfit<-seq(min(data_curve),max(data_curve),length=40)
    yfit<-dnorm(xfit,mean=mean(data_curve),sd=sd(data_curve))
    yfit <- yfit*diff(data_hist$mids[1:2])*length(data_curve)
    lines(xfit, yfit, col="blue", lwd=2)
data_hist
```
\hfill\break
4. Open the iris dataset. Create a subset for each species.
a. Write the codes and its result.
```{r, include= TRUE}
data("iris")
data_iris <- data.frame(iris)
data_iris

data_seto <- subset(data_iris, Species == 'setosa' )
data_seto

data_versi <- subset(data_iris, Species == 'versicolor' )
data_versi

data_virg <- subset(data_iris, Species == 'virginica' )
data_virg
```
\hfill\break
b. Get the mean for every characteristics of each species using colMeans(). Write the codes and its result. Example: setosa <- colMeans(setosa[sapply(setosaDF,is.numeric)])
```{r, include= TRUE}
setosa <- colMeans(data_seto[sapply(data_seto,is.numeric)])
setosa

versicolor <- colMeans(data_versi[sapply(data_versi,is.numeric)])
versicolor

virginica <- colMeans(data_virg[sapply(data_virg,is.numeric)])
virginica
```
\hfill\break
c. Combine all species by using rbind() The table should be look like this:
```{r, include= TRUE}
grp_data <- rbind(setosa, versicolor,virginica)
grp_data

grp_df <- data.frame(grp_data)
grp_df
```
\hfill\break
d  From the data in 4-c: Create the barplot(). Write the codes and its result. The barplot should be like this.
```{r, include= TRUE}
barplot (height= as.matrix(grp_df), main = "Iris Data",
         xlab = "Characteristics",
ylab = "Mean Scores",
beside = T, col = rainbow(3))
```